\documentclass[../../main.tex]{subfiles}
 
\begin{document}

\section{Teaching}

\begin{enumerate}
\item Student Evaluation Summaries and Individual Evaluations ... \textit{All courses taught from Fall 2017-Spring 2018}.
\item American Association of Physics Teachers (AAPT) Workshop for New Professors program.  I attended this workshop for new professors on research-based teaching methods in physics education in Fall 2017.
\item Sample midterm, Computer Logic and Digital Circuit Design
\item Sample midterm and study-guide, Algebra-based Physics I (PHYS135A)
\item Sample midterm and study-guide, Algebra-based Physics II (PHYS135B)
\item Sample midterm and study-guide, Calculus-based Physics I (PHYS150)
\item Sample midterm and study-guide, Calculus-based Physics II (PHYS180)
\item Sample syllabi ... \textit{One syllabus included for each course taught between Fall 2017-Fall 2018}
\item Sample GitHub webpages and databases for teaching materials ... \textit{All courses Fall 2017-Fall 2018}.  I use these databases to store every lecture, PI module, and laboratory activity I've given as a professor.  These databases provide a complete record of my teaching for future use and modification.  Additionally, the databases can be branched into different versions suitable for classes of different skill levels and content focuses.
\item Example Final Assignment (PHYS135A) ... \textit{Final Essay on Venus Transits by Elmer van Butselaar}.  This was a final assignment in PHYS135A, practicing written and oral communication in science.  The student explains how the distance between the Earth and the Sun was first measured.
\item Example Final Assignment (PHYS135B) ... \textit{Final Pres. on Muscle Activation Voltages by Brandon Mai}.  This was a final assignment in PHYS135B, practicing written and oral communication in science.  The student explains human muscles are activated by voltages from the nervous system, and measurements were performed and reported on bicep muscle voltages.
\item Example Final Assignment (PHYS150) ... \textit{Final Essay on Gravity Waves from LIGO by Nick Clarizio}.  This was a final assignment in PHYS150, practicing written and oral communication in science.  The student explains the significance of the experiment that won the 2017 Nobel Prize in physics.
\item Example Final Assignment (PHYS180) ... \textit{Final Essay on Energy Conservation by Brandon Choi}.  This was a final assignment in PHYS180, practicing written and oral communication in science.  The student explains the origins of the law of energy conservation.
\item Example PhET Assignment (PHYS135B/PHYS180) ... \textit{Modeling DC circuits}.  This is an example of a PhET exercise incorporated into the curriculum, in which students use a computer simulation to model a real circuit, verifying their calculations.
\end{enumerate}

\section{Research}

\begin{enumerate}
\item \textit{Curriculum Vitae}
\item \textit{Department of Physics and Astronomy Department guidelines on tenure and promotion}
\item Physics Colloquium slides ... \textit{Whittier College}.  This is a copy of the hour-long lecture I gave to students and faculty at Whittier College at the end of Spring 2019.
\item Physics Colloquium slides ... \textit{California Polytechnic San Luis Obispo}.  This is a copy of the hour-long lecture I gave to students and faculty at California Polytechnic University, San Luis Obispo campus.  Meetings with faculty there were key in advancing the calculations and ideas in the lecture, and the Whittier Colloquium directly benefitted.
\item Colloquium Feedback from Students ... \textit{Maya Eylon and Nick Clarizio}.  Two of my students provided feedback from the Whittier colloquium, and indicated that the lecture benefitted them in several ways.
\item Samples of Recent Scholarship ... \textit{Two scientific peer-reviewed journal articles (primary author)}.  The paper published in the Journal of Cosmology and Astroparticle Physics I claim as my first official publication as a Whittier professor, in satisfaction of the tenure and promotion guidelines of my department.
\item Write-up for DigLibArts on The Primer ... \textit{Created for Prof. Andrea Rehn, DigLibArts}.  Professor Andrea Rehn required me to create a short deliverable for the Primer project, to be shown to other DigLibArts faculty and students.
\end{enumerate}

\section{Service}

\begin{enumerate}
\item Award for Outstanding Organization Advisor ... \textit{For service to CRU}.  I am the first Whittier College professor to win this award, for service to a student organization.
\item Photo of Lecture at Los Nietos Middle School ... \textit{STEM Lecture Nights Outreach Program}.  I gave a public lecture explaining the role of Whittier College in physics research to middle school students and parents.  A local high-school student named Cole Aedo helped me to organize the event, and the principle Shannon Brann-Zelaya is standing to the left of me in the photo.
\end{enumerate}

\section{Advising and Mentoring}

\begin{enumerate}
\item Sample letter of recommendation for Cassady Smith.
\item Sample letter of recommendation for Nicholas Haarlammert.
\end{enumerate}

\end{document}
