\documentclass[../main.tex]{subfiles}
 
\begin{document}

In my first year as an assistant professor at Whittier College, I have had many acheivements.  I have taught courses in introductory physics that have prepared many students for the hard work of becoming physicists and engineers, and I have done my best to convince struggling students to believe in their ability to perform mathematical and scientific calculations.  Large introductory physics courses are objectively difficult to teach, given the wide range of preparation and confidence in mathematics and problem-solving skills of our students.  I take this responsibility seriously, and I enjoy the struggle, failure, and final success of the process of enlightening our students.  It is my hope that the reflections in this document communicate a sincere and authentic desire to teach well, and I encourage other professors to contact me with any questions or helpful advice on that front.  My contact information is listed below.  I would also point out that I have created brand new physics and computer science courses at Whittier, and included never-before-taught content, like firmware development and digital signal processing.  \\ \hspace{0.1cm}

I am proud of the research I've accomplished this year, and how I've been able to involve undergraduates in the research process.  I've brought a new field of physics research to Whittier College, astroparticle physics, and I've involved a diverse set of undergraduates in my firmware and software activities.  I've given colloquia representing Whittier College at other universities, and my students have won fellowships.  We have exciting and promising plans going forward, on a diverse set of projects that will educate students \textit{in all phases of science.}  Finally, I have demonstrated connections to a broader scientific community that is moving ahead with plans to construct a large new scientific instrument at the South Pole, and this will represent new opportunities for Whittier undergraduates. \\ \hspace{0.1cm}

I have put in the effort to serve Whittier College and be a helpful advisor to undergraduates, in a number of ways.  I look forward to learning more about how the school operates, and helping to nurture this institution.  I have helped hire other profesors, and aided students in running an organization.  I have served my department by doing the tasks the senior professors ask me to do regarding recruitment and mentoring.  I've joined the ESAC committee and I've embarked on a suitable and useful research project regarding admissions data.  Finally, I've taken on the role of advising physics majors, with the goal of graduating my first majors by the end of next year. \\ \hspace{0.1cm}

I look forward to growth as a teacher and a scholar, and I'd like to thank the Faculty Personel Committee for taking the time to evaluate this report.  Please contact me with any questions.  Thank you for your consideration and support. \\ \hspace{0.1cm}

Jordan C. Hanson, PhD \\
Assistant Professor, Department of Physics and Astronomy \\
Science and Learning Center, 212 \\
Whittier College \\
562.907.5130 \\
jhanson2@whittier.edu

\end{document}
